Natural Language Interfaces to Structured Data

### 2012-07-11 trunk/tr-nlisurvey/src/document.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ANATOMY OF SYSTEMS                  %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Anatomy of NLI systems}
\label{sec:anatomy}
The main problem to solve is to map user's intent expressed in a natural way
(say unstructured way) to a database query, which is a very structured
expression where there is no room for ambiguity unlike natural language.
As a result, all interfaces must deal with words or terms ``meaning''. This
``meaning'' or semantics is in the end defined in terms of ``database
elements''.

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ANATOMY OF SYSTEMS                  %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Anatomy of NLI systems}
\label{sec:anatomy}
The main problem to solve is to map user's intent expressed in a natural way
(say unstructured way) to a database query, which is a very structured
expression where there is no room for ambiguity unlike natural language.
The problem can be formalized as:
\begin{equation}
f:\left\{
\begin{array}{l}
Q\rightarrow (Q^\prime\times S)^I\\
q\mapsto(q^\prime_i, s_i)_i
\end{array}\right.
\end{equation}
where $q$ is the user's question, $q^\prime_i$ a structured query and $s_i$ a
score associated to the structured query $q^\prime_i$, and used to rank the
query (the index $i\in I=[0,n]$ is the rank).

@@

\begin{figure*}
\centering
\includegraphics[width=12cm]{images/query-language}
\caption{Blabla}
\label{fig:query-languages}
\end{figure*}
